Evaluating the Importance of Initial Conditions for Antarctic Sea Ice Seasonal Predictability with a Fully Coupled Model

### 2025-10-24 analysis/paper/access-ice.qmd
Init needds to come after download.
Adds software citations

execute: 
  echo: false
  warning: false
  message: false
  cache: refresh

@@

```{r zenodo, cache = FALSE}
source(here::here("R/zenodo.R"))
zenodo_init()
zenodo_download_data()
```

@@

>>>>

execute: 
  echo: false
  warning: false
  message: false
  cache: true

@@

```{r zenodo, cache = FALSE}
source(here::here("R/zenodo.R"))
zenodo_download_data()
zenodo_init()
```

@@

## Computational procedures

We performed all analysis in this paper using the R programming language [@rcoreteam2020], using data.table [@dowle2020] and metR [@campitelli2020b] packages.
Significant processing was performed using the CDO command line operators [@schulzweida2023].
All graphics are made using ggplot2 [@wickham2009].
The paper was rendered using knitr and quarto [@xie2015; @allaire2022].

### 2025-10-24 analysis/paper/access-ice.tex
Adds software citations

>>>>

\subsection{Computational procedures}\label{computational-procedures}

We performed all analysis in this paper using the R programming language
\citep{rcoreteam2020}, using data.table \citep{dowle2020} and metR
\citep{campitelli2020b} packages. Significant processing was performed
using the CDO command line operators \citep{schulzweida2023}. All
graphics are made using ggplot2 \citep{wickham2009}. The paper was
rendered using knitr and quarto \citep{xie2015, allaire2022}.
